---
title: "Sneha Kannan's Resume"
author: Sneha Kannan
date: "`r Sys.Date()`"
output:
  pagedown::html_resume:
    css: ['css/styles.css', 'resume']
    # set it to true for a self-contained HTML page but it'll take longer to render
    self_contained: true
---

```{r, include=FALSE}
knitr::opts_chunk$set(
  results='asis', 
  echo = FALSE
)

library(glue)
library(tidyverse)

# ======================================================================
# These variables determine how the the data is loaded and how the exports are
# done.

# Is data stored in google sheets? If no data will be gather from the csvs/
# folder in project
using_googlesheets <- FALSE

# Just the copied URL from the sheet
#positions_sheet_loc <- "https://docs.google.com/spreadsheets/d/14MQICF2F8-vf8CKPF1m4lyGKO6_thG-4aSwat1e2TWc"

# Is this sheet available for anyone to read? If you're using a private sheet
# set this to false and go to gather_data.R and run the data loading manually
# once to cache authentication
#sheet_is_publicly_readable <- TRUE

# Is the goal of this knit to build a document that is exported to PDF? If so
# set this to true to have links turned into footnotes at the end of the
# document
PDF_EXPORT <- TRUE


#CV_PDF_LOC <- "https://github.com/snehakannan/cv/raw/master/skannan_resume.pdf"
#CV_HTML_LOC <- ""


# ======================================================================
# Now we source two external scripts. One contains functions for building the
# text output and the other loads up our data from either googlesheets or csvs

# Functions for building sections from CSV data
source('parsing_functions.R') 

# Load data for CV/Resume
source('gather_data.R')
```



```{r}
# When in export mode the little dots are unaligned, so fix that. 
if(PDF_EXPORT){
  cat("
  <style>
  :root{
    --decorator-outer-offset-left: -6.5px;
  }
  </style>")
}
```


Aside
================================================================================

<!-- ```{r} -->
<!-- # When in export mode the little dots are unaligned, so fix that.  -->
<!-- if(PDF_EXPORT){ -->
<!--   glue("View this CV online with links at _{CV_HTML_LOC}_") -->
<!-- } else { -->
<!--   glue("[<i class='fas fa-download'></i> Download a PDF of this CV]({CV_PDF_LOC})") -->
<!-- } -->
<!-- ``` -->

Contact {#contact}
--------------------------------------------------------------------------------

<!--- <i class="fa fa-envelope"></i> -->
- <i class="fa fa-link"></i> [Website](https://fittingthecurve.netlify.com/)
- <i class="fa fa-github"></i> [Github](http://github.com/snehakannan)
<!--- <i class="fa fa-phone"></i> -->
- <i class="fa fa-linkedin"></i> [Linkedin](https://www.linkedin.com/in/sneha-kannan/)


Skills {#skills}
--------------------------------------------------------------------------------

- <i class="fa fa-laptop"></i> **Programming**: R, Python, PostgreSQL, Java, GitHub

- <i class="fa fa-file-code-o"></i> **Tools**: tidyverse, caret, ggplot2, tidymodels, pandas,  scikit-learn, NumPy, Jupyter Notebook, Microstrategy

- <i class="fa fa-book"></i> **Machine Learning**: Regression & Classification models (Linear & Logistic Regression, Random Forest, Boosting, Support Vector Machines), Model Selection and Evaluation, Hypothesis testing (A/B testing), Clustering, Segmentation, Optimization, MapReduce

Disclaimer {#disclaimer}
--------------------------------------------------------------------------------

Made with the R package [**pagedown**](https://github.com/rstudio/pagedown). 

The source code is available at [github.com/snehakannan/cv](https://github.com/snehakannan/cv).

Last updated on `r Sys.Date()`.


Main
================================================================================

Sneha Kannan {#title}
--------------------------------------------------------------------------------
I am adept at processing large quantities of complex data, feature engineering, building and deploying machine learning models in production by collaborating with product managers, data engineers and software developers. I am seeking a new opportunity to utilize my skills and broaden my experience while I contribute to the growth of the organization.

Work Experience {data-icon=suitcase}
--------------------------------------------------------------------------------
```{r}
print_section(position_data, 'experience')
```

<br/>
<br/>
<br/>

Education {data-icon=graduation-cap data-concise=true}
--------------------------------------------------------------------------------
```{r}
print_section(position_data, 'education')
```

Graduate Projects {data-icon=university data-concise=true}
--------------------------------------------------------------------------------
```{r}
print_section(position_data, 'graduate_projects')
```


